DraftOne

### 2016-06-20 DraftOne.Rmd
Fixing beta_bias, adding coverage_beta

---
title: "DraftOne"
author: "Sarah Koehler"
date: "June 1, 2016"
output: html_document
---

@@

```{r}
# Measure percent bias
beta_bias <- function(df, true_rr){
        fig_bias <- 100 * (mean(df$est) - true_rr) / true_rr
        wang_bias <- 100 * (true_rr - mean(df$est)) / true_rr
        out <- data.frame(fig_bias, wang_bias)
        return(out)
}
beta_bias(rep_df, true_rr = 1.02)
```

>>>>

---
title: "DraftOne"
author: "Sarah Koehler"
date: "June 1, 2016"
output: word_document
---

@@

```{r}
# Measure percent bias
beta_bias <- function(df, true_rr){
        percent_bias <- 100 * (true_rr - mean(exp(df$est))) / true_rr
        out <- data.frame(percent_bias)
        return(out)
}
beta_bias(rep_df, true_rr = 1.02)
```
